---
title: "R-Assignment 4"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Created by Songglod Petchamras (ID: 63130500042)**

### Choose Dataset:
- Top 270 Computer Science/Programming Books (Data from Thomas Konstantin, [Kaggle](https://www.kaggle.com/thomaskonstantin/top-270-rated-computer-science-programing-books)) >> [Using CSV](https://raw.githubusercontent.com/safesit23/INT214-Statistics/main/datasets/prog_book.csv)

### Outlines
1. Explore the dataset
2. Learning function from Tidyverse
3. Transform data with dplyr and finding insight the data
4. Visualization with ggplot2

## Part 1: Explore the dataset

### Load necessary packages
```{r load-pk}
packages <- c("dplyr", "readr", "ggplot2", "scales", "stringr")
lapply(packages, library, character.only = T)
```

### Load dataset
```{r load-dataset}
dt <- read_csv("https://raw.githubusercontent.com/safesit23/INT214-Statistics/main/datasets/prog_book.csv")
```

### Check the head of dataset
```{r check-head}
head(dt)
# 2 columns have an inappropriate data type
```

### Change data type
```{r change-data-type}
dt <- dt %>%
    mutate_at(.vars = c("Reviews", "Number_Of_Pages"), 
              .funs = as.integer) %>%
    mutate(Type = as.factor(Type))
```

### Explore section
```{r explore}
# verify & explore
glimpse(dt)
```

```{r check-na}
# check N/A value
colSums(is.na(dt))
```

```{r summary}
# explore & summary
summary(dt)
```

### In this dataset, it has 271 rows and 7 columns
- Rating
- Reviews
- Book_title
- Description
- Number_of_pages
- Type 
- Price

## Part 2: Learning function from Tidyverse

- Function `geom_vline()` and `geom_hline()` from package [ggplot2](https://ggplot2.tidyverse.org/reference/geom_abline.html)
- These geoms add reference lines (sometimes called rules) to a plot, either horizontal, vertical, or diagonal (specified by slope and intercept). These are useful for annotating plots.
- Use cases are in **Part 4**

## Part 3: Transform data with dplyr and finding insight the data

1. Three book types (26 books) have ratings lower than all books accounted for 10% of all.
- Paperback 19 books
- Hardcover 6 books
- Kindle Edition 1 book

```{r 1}
# 1
result <- dt %>%
    filter(Rating < quantile(Rating, 0.1)) %>%
    group_by(Type) %>%
    summarise(amount = n(),
              avg.rating = mean(Rating),
              avg.price = mean(Price)) %>%
    arrange(desc(amount))

# view
result %>% mutate(avg.price = scales::dollar(avg.price))

# output
result %>% summarise(total = sum(amount))
```

2. These books have "C++" in the title (these all books are related to the C++ language). Based on the output, C++ Primer has the lowest price-per-page at $0.062/1 page.

```{r 2}
# 2
cplus_table <- dt %>%
    filter(str_detect(Book_title, pattern = "(C|c)\\+\\+")) %>%
    select(-Description, -Reviews, -Type) %>%
    mutate(price.per.page = Price/Number_Of_Pages) %>%
    arrange(price.per.page)

# view
cplus_table %>% mutate(Price = scales::dollar(Price))

# output
cplus_table %>% 
    mutate(Price = scales::dollar(Price)) %>%
    filter(price.per.page == min(price.per.page))
```

3. These books have “Python” in the title (these all books are related to the Python language). Based on the output, four books have ratings below 25% among all Python books.

```{r 3}
# 3
py_table <- dt %>%
    filter(str_detect(Book_title, pattern = "(P|p)ython")) %>%
    select(-Description, -Reviews, -Type) %>%
    arrange(desc(Rating))

# view
py_table %>% mutate(Price = scales::dollar(Price))

# output
py_table %>% 
    filter(Rating < quantile(Rating, 0.25)) %>%
    mutate(Price = scales::dollar(Price)) %>%
    arrange(Rating)
```

4. These books have "Game" in the title (All books are related to Game programming or design). Based on the output, "3D Game Engine Architecture: Engineering Real-Time Applications with Wild Magic" has the lowest rating of all at 3.76.

```{r 4}
# 4
game_table <- dt %>%
    filter(str_detect(Book_title, pattern = "(G|g)ame")) %>%
    select(-Description, -Reviews) %>%
    arrange(desc(Price))

# view
game_table %>% mutate(Price = scales::dollar(Price))

# output
game_table %>%
    filter(boxplot.stats(game_table$Price)$out == Price) %>%
    mutate(Price = scales::dollar(Price))
```

5. These books have "Algorithm" in the title (All books are related to algorithms). Based on the output, The most book type is the hardcover type.

```{r 5}
# 5
algo_table <- dt %>%
    filter(str_detect(Book_title, pattern = "(A|a)lgorithm")) %>%
    select(-Description, -Reviews) %>%
    group_by(Type) %>%
    summarise(amount = n(),
              avg.rating = mean(Rating),
              avg.price = mean(Price))

# view
algo_table %>% mutate(avg.price = scales::dollar(avg.price))

# output
algo_table %>%
    filter(amount == max(amount)) %>%
    mutate(avg.price = scales::dollar(avg.price))
```

6. The number of books that have high prices is 27 books accounted for 10% of all.
- Hardcover 21 books
- Paperback 5 books
- Boxed Set - Hardcover 1 book

```{r 6}
# 6
dt %>%
    select(-Reviews, -Description) %>%
    filter(Price > quantile(Price, 0.9)) %>%
    group_by(Type) %>%
    summarise(amount = n(),
              avg.rating = mean(Rating),
              avg.price = mean(Price)) %>%
    arrange(desc(amount)) %>%
    mutate(avg.price = scales::dollar(avg.price))
```

## Part 4: Data Visualization with ggplot2

1. The graph shows the frequency of books in rating, most of all books have ratings between 4.0 and 4.2

```{r fig.1}
# fig. 1
dt %>% 
    ggplot(aes(x = Rating)) + 
    geom_histogram(binwidth = 0.2) +
    aes(fill = Type) +
    geom_vline(xintercept = mean(dt$Rating), linetype = "dashed") +
    scale_x_continuous(breaks = seq(3, 5, 0.2)) +
    scale_y_continuous(breaks = seq(0, 100, 10)) +
    labs(title = "Frequency of books in rating",
         caption = "dashed line = mean line",
         tag = "Fig. 1") +
    theme_bw()
```

2. The graph shows the correlation of Price and Number of Pages compared between Hardcover and Paperback.
- Hardcover: If have more pages, higher prices
- Paperback: prices and number of pages, most of all stick as a group and below the mean line

```{r fig.2}
# fig. 2
dt %>%
    filter(Number_Of_Pages < 1500 & Price < 150) %>%
    filter(Type == "Hardcover" | Type == "Paperback") %>%
    ggplot(aes(x = Number_Of_Pages, y = Price)) +
    aes(color = Rating, size = Reviews) +
    geom_point() + 
    scale_color_distiller(palette = "RdPu") +
    facet_wrap(~Type) +
    geom_hline(yintercept = mean(dt$Price), linetype = "dashed", alpha = 0.5) +
    geom_vline(xintercept = mean(dt$Number_Of_Pages), linetype = "dashed", alpha = 0.5) +
    scale_x_continuous(breaks = seq(0, 1200, 200)) +
    scale_y_continuous(breaks = seq(0, 150, 10)) +
    stat_ellipse() +
    labs(title = "The correlation of Price and Number of Pages", 
         subtitle = "Comparison between the correlation of Price and Number of Pages in Hardcover and Paperback",
         caption = "dashed line = mean line",
         tag = "Fig. 2") +
    theme_bw()
```
