---
title: "Hypothesis testing"
output: github_document
---

## Prerequisite

### Loading the necessary packages

```{r load-pkg}
packages <- c("dplyr", "readr", "scales")
lapply(packages, library, character.only = T)
```

### Import the dataset

```{r import-dataset}
movies <- read_csv("https://raw.githubusercontent.com/sit-2021-int214/004-movie-industry/main/movie_industry/csv/cleaned_dataset/movies_cleaned.csv")
```

### Observe the dataset

```{r observe-stage}
# observe dataset and data type
glimpse(movies)
```

### Convert to the appropriate datatype

```{r convert-stage}
# convert data type
movies <- movies %>%
    mutate(year = format(year, format = "%Y")) %>%
    mutate(released.country = as.factor(released.country)) %>%
    mutate_at(.vars = c("genre", "rating", "country"), .funs = as.factor) %>%
    mutate_at(.vars = c("votes", "runtime"), .funs = as.integer)
```

### Verifying the datatype

```{r check-stage}
# verify data type
glimpse(movies)
```

### Summary dataset

```{r summary}
summary(movies)
```

## Prepare for Hypothesis testing

-   Define the problems
-   Define the confidence level for your problems
-   Null hypothesis & Alternative hypothesis

**Problem** <br>
The film director claims that making an action movie can earn \$145.51 million or more, but the marketing department calculates the earnings of 500 random action movies over the years. The average earned only \$129.58 million. The population standard deviation is \$247.52 million. At a significance level of 95%, is it possible that the marketing department could reject the director from making the action film?

1.  Count an action movie in dataset

```{r population}
pop.n <- movies %>%
    filter(gross > 0) %>%
    group_by(genre) %>%
    summarise(count = n()) %>%
    filter(genre == "Action")

pop.n %>%
    mutate(count = scales::comma(count))

pop.n <- pop.n$count
```

2.  Finding the population mean gross of an action movie

```{r pop-mean}
pop.mean <- movies %>%
    filter(gross > 0) %>%
    group_by(genre) %>%
    summarise(pop.mean.gross = mean(gross)) %>%
    filter(genre == "Action")

pop.mean %>%
    mutate(pop.mean.gross = scales::dollar(pop.mean.gross))

pop.mean <- round(pop.mean$pop.mean.gross, 2)
```

3.  Finding the population mean gross of an action movie

```{r pop-sd}
pop.sd <- movies %>%
    filter(gross > 0) %>%
    group_by(genre) %>%
    summarise(pop.sd.gross = sd(gross)) %>%
    filter(genre == "Action")
pop.sd %>%
    mutate(pop.sd.gross = scales::dollar(pop.sd.gross))

pop.sd <- round(pop.sd$pop.sd.gross, 2)
```

4.  Define the sample size

```{r sample-n}
sample.n <- 500
```

5.  Finding the sample mean gross of an action movie

```{r find-sample-mean}
# sample.data <- movies %>%
#     filter(gross > 0) %>%
#     filter(genre == "Action") %>%
#     select(name, gross)
# 
# sample.mean <- mean(sample.data$gross[sample(1:nrow(sample.data), sample.n)])
# sample.mean <- round(sample.mean, 2)
```

```{r sample-mean}
scales::dollar(sample.mean)
```

6.  Define the confidence level for the hypothesis testing <br> So, we will use 95% confidence level

```{r define-alpha}
alpha <- 0.05
```

## Hypothesis testing

1.  State the null and alternative hypothesis from the problem

    -   Ho: u >= \$145.51 Million <br>
    -   Ha: u \< \$145.51 Million

    this is the left-tailed test

2.  finding the z alpha

```{r z-alpha}
z.alpha <- qnorm(alpha)
z.alpha
```

3.  Calculating the standard error

```{r standard-error}
SE <- pop.sd/sqrt(sample.n)
SE
```

4.  Calculating the z.c

```{r z-c}
z.c <- (sample.mean - pop.mean)/SE
z.c
```

5.  Finding the p-value

```{r p-value}
p.value <- pnorm(z.c)
p.value
```

6.  Testing the hypothesis by z-test or p-value

```{r z-test}
# by z-test
if (z.c >= z.alpha) {
    print("Failed to reject Ho")
} else {
    print("Reject Ho")
}
```

```{r p-value-test}
# by p-value
if (p.value >= alpha) {
    print("Failed to reject Ho")
} else {
    print("Reject Ho")
}
```

7.  Conclusion

The marketing department cannot refuse a director's request to make an action movie.

